Interactive Curvature Tensor Visualization on Digital Surfaces\thanks{This work has been mainly funded by \textsc{DigitalSnow} ANR-11-BS02-009, \textsc{KIDICO} ANR-2010-BLAN-0205 and \textsc{PRIMES Labex} ANR-11-LABX-0063/ ANR-11-IDEX-0007 research grants.}

### 2016-01-25 latex/article.tex
added raisebox and "..." to figure 5

\begin{figure}
  \vspace{-0.35cm}
  \begin{center}
    {\includegraphics[width=4.0cm]{figs/approx-naive}}
    {\includegraphics[width=4.0cm]{figs/approx-hierarchical}}
    {\includegraphics[width=4.0cm]{figs/approx-dynamic}}
  \end{center}
  \vspace{-0.35cm}
  \caption{\txtblue{
  	Here are the three approaches we used to evaluate the integrand.
  	(\emph{left}) is the naive approach, where we sum all the digital points that are inside the integrand domain
  	(\emph{middle}) shows the hierarchical decomposition of the ball, thus limiting the number of texture probes to do.
  	(\emph{right}) illustrates the dynamic approach, we probe the textures at a higher resolution and we refine it at each frame until we reach the finer level.
    }}\label{fig:approx}
  \vspace{-0.35cm}
\end{figure}

>>>>

\begin{figure}
  \vspace{-0.35cm}
  \begin{center}
    \raisebox{60pt}{\includegraphics[width=3.7cm]{figs/approx-naive}}
    \hfill
    \raisebox{60pt}{\includegraphics[width=3.7cm]{figs/approx-hierarchical}}
    \hfill
    \includegraphics[width=3.7cm]{figs/approx-dynamic}
  \end{center}
  \vspace{-0.35cm}
  \caption{\txtblue{
  	Here are the three approaches we used to evaluate the integrand.
  	(\emph{left}) is the naive approach, where we sum all the digital points that are inside the integrand domain
  	(\emph{middle}) shows the hierarchical decomposition of the ball, thus limiting the number of texture probes to do.
  	(\emph{right}) illustrates the dynamic approach, we probe the textures at a higher resolution and we refine it at each frame until we reach the finer level.
    }}\label{fig:approx}
  \vspace{-0.35cm}
\end{figure}
